Efficient Constructions of Prefer-Max Sequences and of Infinite de Bruijn Sequences

### 2017-01-08 paper.tex
...

\begin{algorithm}
Repeatedly append the maximal symbol over the alphabet $0,\dots,k-1$ such that the word formed by the $n$ most recent symbols is new (in the first $n$ steps, act as if thee are $n$ invisible zeros before the sequence). Stop after appending $n$ consecutive zeros. 
\caption{The $(k,n)$-prefer-max sequence.}
\label{pref-max}
\end{algorithm}

>>>>

\begin{algorithm}
Repeatedly append the maximal symbol over the alphabet $0,\dots,k-1$ such that the word formed by the $n$ most recent symbols is new. In the first $n$ steps, act as if thee are $n$ invisible zeros before the sequence. Stop after appending $n$ consecutive zeros. 
\caption{The $(k,n)$-prefer-max sequence.}
\label{pref-max}
\end{algorithm}
